Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-15 paper/v2/paper-edited.tex
fix
adding correct style
adding categories and terms

\documentclass{sig-alternate-10pt}

@@

@@

%\category{CR-number}{subcategory}{third-level}
%% general terms are not compulsory anymore,
%% you may leave them out
%\terms
%term1, term2
%\keywords
%keyword1, keyword2

@@

@@

Since, by default, routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
\begin{code}
\Define transit(X,Y) = \Enter(X \OR Y) \AND \Exit(X \OR Y)
\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
\end{code}
\noindent
Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.

@@

\begin{figure*}\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{\large Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline

@@

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{\large Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
    \None          & = & \emptyset \\
    \Internal      & = & \In^+ \\
    \Only(X)       & = & \Any \cap X^* \\
    \Never(X)      & = & \Any \cap (!X)^* \\
    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    \Novalley(\vec{X}) & = & \Any ~ \cap \\
                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]

@@

  \hdr{\large Topology}{}
  \vspace*{-2\baselineskip}

@@

  \hdr{\large Policy Automata}{}
  \vspace*{-0.5\baselineskip}

@@

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$4$}{right of=3}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{in}{}
    \transition{2}{2}{A,C,D,E}{loop above}
    \transition{2}{3}{B}{}
    \transition{3}{3}{B}{loop above}
    \transition{3}{2}{A,C,D,E}{bend left}
    \transition{3}{4}{W}{}
  \end{tikzpicture}
  \end{minipage}
  %
  ~~
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Product Graph IR}{}
  \vspace*{-1\baselineskip}
  %
  \includegraphics[width=.65\columnwidth]{figures/productgraph}
  \end{minipage}

@@

For example, recall the data center example from \S\ref{sec:motivation}, with the policy: 
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).
>>>>>>> minor edits

>>>>

%\documentclass{sig-alternate-10pt}
\documentclass[10pt]{sigalternate052015}

@@

\setcopyright{acmcopyright}
\conferenceinfo{SIGCOMM '16}{August 22--26, 2016, Florianopolis, Brazil}

@@

@@

%=====================================================
%
%
%  **Keywords**
%
%
%=====================================================

%\category{CR-number}{subcategory}{third-level}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003068.10003073.10003075</concept_id>
<concept_desc>Networks~Network control algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Network control algorithms}
\ccsdesc[300]{Software and its engineering~Domain specific languages}

\printccsdesc

\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault tolerance}

%% general terms are not compulsory anymore,
%% you may leave them out
%\terms Network Programming Language, Distributed Program Synthesis
%\keywords Propane Language, BGP, Synthesis, Compilation

@@

Since, by default, routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
\begin{code}
\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
\end{code}
\noindent
Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.

@@

\begin{figure*}[t]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline

@@

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
    \None          & = & \emptyset \\
    \Internal      & = & \In^+ \\
    \Only(X)       & = & \Any \cap X^* \\
    \Never(X)      & = & \Any \cap (!X)^* \\
    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    \Novalley(\vec{X}) & = & \Any ~ \cap \\
                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]

@@

  \hdr{Topology}{}
  \vspace*{-2\baselineskip}

@@

  \hdr{Policy Automata}{}
  \vspace*{-0.5\baselineskip}

@@

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$4$}{right of=3}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{in}{}
    \transition{2}{2}{A,C,D,E}{loop above}
    \transition{2}{3}{B}{}
    \transition{3}{3}{B}{loop above}
    \transition{3}{2}{A,C,D,E}{bend left}
    \transition{3}{4}{W}{}
  \end{tikzpicture}
  \end{minipage}
  %
  ~~
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Product Graph IR}{}
  \vspace*{-1\baselineskip}
  %
  \includegraphics[width=.65\columnwidth]{figures/productgraph}
  \end{minipage}

@@

For example, recall the data center example from \S\ref{sec:motivation}, with the policy: 
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).
